A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-21 ms.tex
Modify motivation of uniformly illuminated sky
In ms.tex,

(*) Change first sentence in S7.1 motivating the simulation of uniformly
illuminated sky

In ApJ_referee_report_1_addressed.txt,

(*) Address flux scale question in the referee report

{\bf Having examined the role foregrounds play in determining the delay power spectrum obtained with an interferometer array, we turn our attention to another crucial factor, namely, the power pattern of the antenna (refer to equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform}). Unlike the flagging of the edges of the coarse sub--bands described earlier in this paper, we assume an ideal flat passband over the entire 30.72~MHz bandwidth while still applying a {\it Blackman--Harris} window function}.

@@

{\bf In the following discussion, we assume there are no random delay fluctuations in the MWA tile beamforming process. The model power pattern so obtained is different from the one we used earlier, but the former still serves as a good reference (Figure~\ref{fig:power_pattern}) for the present discussion. Hence, we do not plot the new power pattern model obtained with ideal beamforming.

The brightness distribution on the sky was fixed to be a constant equal to the mean over the whole sky at 185~MHz with no spectral variation. This helps isolate the signatures of the antenna power pattern from those of the foregrounds.

>>>>

{\bf Having examined the role foregrounds play in determining the delay power spectrum obtained with an interferometer array, we turn our attention to another crucial factor, namely, the power pattern of the antenna (refer to equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform}). In the following analysis, unlike the flagging of the edges of the coarse sub--bands described earlier in this paper, we assume an ideal flat passband over the entire 30.72~MHz bandwidth while still applying a {\it Blackman--Harris} window function. We also assume there are no random delay fluctuations in the MWA tile beamforming process}.

@@

{\bf In order to confirm that the {\it pitchfork} effect is independent of the specific foreground model chosen in our study, we also simulated the response to a uniformly illuminated sky. The brightness distribution on the sky was fixed to be a constant equal to the mean over the whole sky at 185~MHz with no spectral variation. This helps isolate the signatures of the antenna power pattern from those of the foregrounds.

 % In the following discussion, we assume there are no random delay fluctuations in the MWA tile beamforming process. The model power pattern so obtained is different from the one we used earlier, but the former still serves as a good reference (Figure~\ref{fig:power_pattern}) for the present discussion. Hence, we do not plot the new power pattern model obtained with ideal beamforming.
